Unemployment Effects

### 2020-05-05 analysis.Rmd
making progress

library(rsconnect)
library(stargazer)
library(plyr)
library(plm)
library(wfe)
library(tidyverse)
```

@@

shp.fit.pooling.tig.ext <- plm(trust_in_government ~ unemployed, 
                        data = shp,
                        index = c("unit", "time"),
                        model = "pooling")

shp.fit.pooling.swd.ext <- plm(satisfaction_with_democracy ~ unemployed, 
                        data = shp,
                        index = c("unit", "time"),
                        model = "pooling")

shp.fit.pooling.ls.ext <- plm(life_satisfaction ~ unemployed, 
                        data = shp,
                        index = c("unit", "time"),
                        model = "pooling")

@@

liss.fit.pooling.tig.ext <- plm(trust_in_government ~ unemployed, 
                        data = liss,
                        index = c("unit", "time"),
                        model = "pooling")

liss.fit.pooling.swd.ext <- plm(satisfaction_with_democracy ~ unemployed, 
                        data = liss,
                        index = c("unit", "time"),
                        model = "pooling")

liss.fit.pooling.ls.ext <- plm(life_satisfaction ~ unemployed, 
                        data = liss,
                        index = c("unit", "time"),
                        model = "pooling")

@@

stargazer(shp.fit.pooling.tig.ext, shp.fit.pooling.control.tig.ext, shp.fit.pooling.swd.ext, shp.fit.pooling.control.swd.ext, shp.fit.pooling.ls.ext, shp.fit.pooling.control.ls.ext, liss.fit.pooling.tig.ext, liss.fit.pooling.control.tig.ext, liss.fit.pooling.swd.ext, liss.fit.pooling.control.swd.ext, liss.fit.pooling.ls.ext, liss.fit.pooling.control.ls.ext,
          type = "latex",
          out="./extension-table-1.tex",
          omit.stat=c("LL","ser","f","adj.rsq"),
          header = FALSE,
          font.size = "tiny",
          digits = 2,
          column.sep.width = "-10pt",
          title = "SHP Switzerland and LISS Netherlands: pooled models with lagged unemployment",
          column.labels = c("(M1)", "(M2)", "(M3)", "(M4)", "(M5)", "(M6)", "(M7)", "(M8)", "(M9)", "(M10)", "(M11)", "(M12)"), 
          covariate.labels = c("Unemployed", "Lagged Unemployed", "Age", "Education", "Member", "UE:Lagged UE"),
          dep.var.labels = c("trust in government", "statisfaction with democracy", "life satisfaction", "trust in government", "satisfaction with democracy", "life satisfaction"),
          model.names = FALSE,
          model.numbers = FALSE
          )
```

@@

shp.fit.fe.tig.ext <- plm(trust_in_government ~ unemployed, 
                        data = shp,
                        index = c("unit", "time"),
                        model = "within")

shp.fit.fe.swd.ext <- plm(satisfaction_with_democracy ~ unemployed, 
                        data = shp,
                        index = c("unit", "time"),
                        model = "within")

shp.fit.fe.ls.ext <- plm(life_satisfaction ~ unemployed, 
                        data = shp,
                        index = c("unit", "time"),
                        model = "within")

@@

liss.fit.fe.tig.ext <- plm(trust_in_government ~ unemployed, 
                        data = liss,
                        index = c("unit", "time"),
                        model = "within")

liss.fit.fe.swd.ext <- plm(satisfaction_with_democracy ~ unemployed, 
                        data = liss,
                        index = c("unit", "time"),
                        model = "within")

liss.fit.fe.ls.ext <- plm(life_satisfaction ~ unemployed, 
                        data = liss,
                        index = c("unit", "time"),
                        model = "within")

@@

stargazer(shp.fit.fe.tig.ext, shp.fit.fe.control.tig.ext, shp.fit.fe.swd.ext, shp.fit.fe.control.swd.ext, shp.fit.fe.ls.ext, shp.fit.fe.control.ls.ext, liss.fit.fe.tig.ext, liss.fit.fe.control.tig.ext, liss.fit.fe.swd.ext, liss.fit.fe.control.swd.ext, liss.fit.fe.ls.ext, liss.fit.fe.control.ls.ext,
          type = "latex",
          out="./extension-table-2.tex",
          omit.stat=c("LL","ser","f","adj.rsq"),
          header = FALSE,
          font.size = "tiny",
          digits = 2,
          label = "table-2",
          column.sep.width = "-10pt",
          title = "SHP Switzerland and LISS Netherlands: fixed effects models with lagged unemployment",
          column.labels = c("(M13)", "(M14)", "(M15)", "(M16)", "(M17)", "(M18)", "(M19)", "(M20)", "(M21)", "(M22)", "(M23)", "(M24)"),
          covariate.labels = c("Unemployed", "Lagged Unemployed", "Age", "Education", "Member", "UE:Lagged UE"),
          dep.var.labels = c("trust in government", "statisfaction with democracy", "life satisfaction", "trust in government", "satisfaction with democracy", "life satisfaction"),
          model.names = FALSE,
          model.numbers = FALSE
          )
```

@@

shp.fit.wfe.tig.ext <- wfe(trust_in_government ~ unemployed, 
                        data = shp,
                        treat = "unemployed",
                       unit.index = "unit", time.index = "time", method = "unit",
               qoi = "ate", estimator =NULL, hetero.se=TRUE, auto.se=TRUE,
               White = TRUE, White.alpha = 0.05, verbose = TRUE)

shp.fit.wfe.swd.ext <- wfe(satisfaction_with_democracy ~ unemployed, 
                        data = shp,
                        treat = "unemployed",
                       unit.index = "unit", time.index = "time", method = "unit",
               qoi = "ate", estimator =NULL, hetero.se=TRUE, auto.se=TRUE,
               White = TRUE, White.alpha = 0.05, verbose = TRUE)

shp.fit.wfe.ls.ext <- wfe(life_satisfaction ~ unemployed, 
                        data = shp,
                        treat = "unemployed",
                      unit.index = "unit", time.index = "time", method = "unit",
               qoi = "ate", estimator =NULL, hetero.se=TRUE, auto.se=TRUE,
               White = TRUE, White.alpha = 0.05, verbose = TRUE)

@@

liss.fit.wfe.tig.ext <- wfe(trust_in_government ~ unemployed, 
                        data = liss,
                        treat = "unemployed",
                        unit.index = "unit", time.index = "time", method = "unit",
               qoi = "ate", estimator =NULL, hetero.se=TRUE, auto.se=TRUE,
               White = TRUE, White.alpha = 0.05, verbose = TRUE)

liss.fit.wfe.swd.ext <- wfe(satisfaction_with_democracy ~ unemployed, 
                        data = liss,
                        treat = "unemployed",
                        unit.index = "unit", time.index = "time", method = "unit",
               qoi = "ate", estimator =NULL, hetero.se=TRUE, auto.se=TRUE,
               White = TRUE, White.alpha = 0.05, verbose = TRUE)

liss.fit.wfe.ls.ext <- wfe(life_satisfaction ~ unemployed, 
                        data = liss,
                        treat = "unemployed",
                       unit.index = "unit", time.index = "time", method = "unit",
               qoi = "ate", estimator =NULL, hetero.se=TRUE, auto.se=TRUE,
               White = TRUE, White.alpha = 0.05, verbose = TRUE)

@@

@@

  stargazer(p1, p1, p2, p2, p3, p3, p1, p1, p2, p2, p3, p3,
    coef = list(as.numeric(summary(shp.fit.wfe.tig.ext)[2]$coefficients[,1]),
                as.numeric(summary(shp.fit.wfe.control.tig.ext)[2]$coefficients[,1]),
                as.numeric(summary(shp.fit.wfe.swd.ext)[2]$coefficients[,1]),
                as.numeric(summary(shp.fit.wfe.control.swd.ext)[2]$coefficients[,1]),
                as.numeric(summary(shp.fit.wfe.ls.ext)[2]$coefficients[,1]),
                as.numeric(summary(shp.fit.wfe.control.ls.ext)[2]$coefficients[,1]),

                as.numeric(summary(liss.fit.wfe.tig.ext)[2]$coefficients[,1]),
                as.numeric(summary(liss.fit.wfe.control.tig.ext)[2]$coefficients[,1]),
                as.numeric(summary(liss.fit.wfe.swd.ext)[2]$coefficients[,1]),
                as.numeric(summary(liss.fit.wfe.control.swd.ext)[2]$coefficients[,1]),
                as.numeric(summary(liss.fit.wfe.ls.ext)[2]$coefficients[,1]),
                as.numeric(summary(liss.fit.wfe.control.ls.ext)[2]$coefficients[,1])

                ),
    se = list(as.numeric(summary(shp.fit.wfe.tig.ext)[2]$coefficients[,2]),
                as.numeric(summary(shp.fit.wfe.control.tig.ext)[2]$coefficients[,2]),
                as.numeric(summary(shp.fit.wfe.swd.ext)[2]$coefficients[,2]),
                as.numeric(summary(shp.fit.wfe.control.swd.ext)[2]$coefficients[,2]),
                as.numeric(summary(shp.fit.wfe.ls.ext)[2]$coefficients[,2]),
                as.numeric(summary(shp.fit.wfe.control.ls.ext)[2]$coefficients[,2]),

                as.numeric(summary(liss.fit.wfe.tig.ext)[2]$coefficients[,2]),
                as.numeric(summary(liss.fit.wfe.control.tig.ext)[2]$coefficients[,2]),
                as.numeric(summary(liss.fit.wfe.swd.ext)[2]$coefficients[,2]),
                as.numeric(summary(liss.fit.wfe.control.swd.ext)[2]$coefficients[,2]),
                as.numeric(summary(liss.fit.wfe.ls.ext)[2]$coefficients[,2]),
                as.numeric(summary(liss.fit.wfe.control.ls.ext)[2]$coefficients[,2])
              ),
    t = list(as.numeric(summary(shp.fit.wfe.tig.ext)[2]$coefficients[,3]),
                as.numeric(summary(shp.fit.wfe.control.tig.ext)[2]$coefficients[,3]),
                as.numeric(summary(shp.fit.wfe.swd.ext)[2]$coefficients[,3]),
                as.numeric(summary(shp.fit.wfe.control.swd.ext)[2]$coefficients[,3]),
                as.numeric(summary(shp.fit.wfe.ls.ext)[2]$coefficients[,3]),
                as.numeric(summary(shp.fit.wfe.control.ls.ext)[2]$coefficients[,3]),

                as.numeric(summary(liss.fit.wfe.tig.ext)[2]$coefficients[,3]),
                as.numeric(summary(liss.fit.wfe.control.tig.ext)[2]$coefficients[,3]),
                as.numeric(summary(liss.fit.wfe.swd.ext)[2]$coefficients[,3]),
                as.numeric(summary(liss.fit.wfe.control.swd.ext)[2]$coefficients[,3]),
                as.numeric(summary(liss.fit.wfe.ls.ext)[2]$coefficients[,3]),
                as.numeric(summary(liss.fit.wfe.control.ls.ext)[2]$coefficients[,3])

             ),  
    p = list(as.numeric(summary(shp.fit.wfe.tig.ext)[2]$coefficients[,4]),
                as.numeric(summary(shp.fit.wfe.control.tig.ext)[2]$coefficients[,4]),
                as.numeric(summary(shp.fit.wfe.swd.ext)[2]$coefficients[,4]),
                as.numeric(summary(shp.fit.wfe.control.swd.ext)[2]$coefficients[,4]),
                as.numeric(summary(shp.fit.wfe.ls.ext)[2]$coefficients[,4]),
                as.numeric(summary(shp.fit.wfe.control.ls.ext)[2]$coefficients[,4]),

                as.numeric(summary(liss.fit.wfe.tig.ext)[2]$coefficients[,4]),
                as.numeric(summary(liss.fit.wfe.control.tig.ext)[2]$coefficients[,4]),
                as.numeric(summary(liss.fit.wfe.swd.ext)[2]$coefficients[,4]),
                as.numeric(summary(liss.fit.wfe.control.swd.ext)[2]$coefficients[,4]),
                as.numeric(summary(liss.fit.wfe.ls.ext)[2]$coefficients[,4]),
                as.numeric(summary(liss.fit.wfe.control.ls.ext)[2]$coefficients[,4])
             ),  
    type = "latex",
    out="./extension-table-3.tex",
    omit.stat = "all",
    notes = "SEs in parentheses. Columns 25-30 are from the SHP survey and columns 31-36 are from the LISS survey.",
    notes.append = TRUE,
    font.size = "tiny",
    digits = 2,
    column.sep.width = "-10pt", 
    title = "SHP Switzerland and LISS Netherlands: weighted fixed effects models",
    digit.separator="",
    rownames = FALSE,
    column.labels = c("(M25)", "(M26)", "(M27)", "(M28)", "(M29)", "(M30)", "(M31)", "(M32)", "(M33)", "(M34)", "(M35)", "(M36)"), 
    model.names = FALSE,
    model.numbers = FALSE,
    star.cutoffs=c(0.05,0.01,0.001),
    covariate.labels = c("Unemployed", "Lagged Unemployed", "Age", "Education", "Member", "UE:Lagged UE"),
    dep.var.labels = c("trust in government", "statisfaction with democracy", "life satisfaction", "trust in government", "satisfaction with democracy", "life satisfaction"),
    header = FALSE
    )  
```

>>>>

library(rsconnect)
library(stargazer)
library(plyr)
library(plm)
library(wfe)
library(berryFunctions)
library(tidyverse)
```

@@

shp.fit.pooling.tig.ext <- plm(trust_in_government ~ unemployed * lagged_unemployed, 
                        data = shp,
                        index = c("unit", "time"),
                        model = "pooling")

shp.fit.pooling.swd.ext <- plm(satisfaction_with_democracy ~ unemployed * lagged_unemployed, 
                        data = shp,
                        index = c("unit", "time"),
                        model = "pooling")

shp.fit.pooling.ls.ext <- plm(life_satisfaction ~ unemployed * lagged_unemployed, 
                        data = shp,
                        index = c("unit", "time"),
                        model = "pooling")

@@

liss.fit.pooling.tig.ext <- plm(trust_in_government ~ unemployed * lagged_unemployed, 
                        data = liss,
                        index = c("unit", "time"),
                        model = "pooling")

liss.fit.pooling.swd.ext <- plm(satisfaction_with_democracy ~ unemployed * lagged_unemployed, 
                        data = liss,
                        index = c("unit", "time"),
                        model = "pooling")

liss.fit.pooling.ls.ext <- plm(life_satisfaction ~ unemployed * lagged_unemployed, 
                        data = liss,
                        index = c("unit", "time"),
                        model = "pooling")

@@

stargazer(shp.fit.pooling.tig.ext, shp.fit.pooling.control.tig.ext, shp.fit.pooling.swd.ext, shp.fit.pooling.control.swd.ext, shp.fit.pooling.ls.ext, shp.fit.pooling.control.ls.ext, liss.fit.pooling.tig.ext, liss.fit.pooling.control.tig.ext, liss.fit.pooling.swd.ext, liss.fit.pooling.control.swd.ext, liss.fit.pooling.ls.ext, liss.fit.pooling.control.ls.ext,
          type = "latex",
          out="./extension-table-1.tex",
          omit.stat=c("LL","ser","f","adj.rsq"),
          header = FALSE,
          font.size = "tiny",
          digits = 2,
          column.sep.width = "-10pt",
          title = "SHP Switzerland and LISS Netherlands: pooled models with lagged unemployment",
          column.labels = c("(M1)", "(M2)", "(M3)", "(M4)", "(M5)", "(M6)", "(M7)", "(M8)", "(M9)", "(M10)", "(M11)", "(M12)"), 
          covariate.labels = c("Unemployed", "Lagged Unemployed", "UE:Lagged UE", "Age", "Education", "Member"),
          dep.var.labels = c("trust in government", "statisfaction with democracy", "life satisfaction", "trust in government", "satisfaction with democracy", "life satisfaction"),
          dep.var.caption = c("SHP, LISS"),
          model.names = FALSE,
          model.numbers = FALSE,
          order = c(1,2,6,3,4,5)
          )
```

@@

shp.fit.fe.tig.ext <- plm(trust_in_government ~ unemployed * lagged_unemployed, 
                        data = shp,
                        index = c("unit", "time"),
                        model = "within")

shp.fit.fe.swd.ext <- plm(satisfaction_with_democracy ~ unemployed * lagged_unemployed, 
                        data = shp,
                        index = c("unit", "time"),
                        model = "within")

shp.fit.fe.ls.ext <- plm(life_satisfaction ~ unemployed * lagged_unemployed, 
                        data = shp,
                        index = c("unit", "time"),
                        model = "within")

@@

liss.fit.fe.tig.ext <- plm(trust_in_government ~ unemployed * lagged_unemployed, 
                        data = liss,
                        index = c("unit", "time"),
                        model = "within")

liss.fit.fe.swd.ext <- plm(satisfaction_with_democracy ~ unemployed * lagged_unemployed, 
                        data = liss,
                        index = c("unit", "time"),
                        model = "within")

liss.fit.fe.ls.ext <- plm(life_satisfaction ~ unemployed * lagged_unemployed, 
                        data = liss,
                        index = c("unit", "time"),
                        model = "within")

@@

stargazer(shp.fit.fe.tig.ext, shp.fit.fe.control.tig.ext, shp.fit.fe.swd.ext, shp.fit.fe.control.swd.ext, shp.fit.fe.ls.ext, shp.fit.fe.control.ls.ext, liss.fit.fe.tig.ext, liss.fit.fe.control.tig.ext, liss.fit.fe.swd.ext, liss.fit.fe.control.swd.ext, liss.fit.fe.ls.ext, liss.fit.fe.control.ls.ext,
          type = "latex",
          out="./extension-table-2.tex",
          omit.stat=c("LL","ser","f","adj.rsq"),
          header = FALSE,
          font.size = "tiny",
          digits = 2,
          label = "table-2",
          column.sep.width = "-10pt",
          title = "SHP Switzerland and LISS Netherlands: fixed effects models with lagged unemployment",
          column.labels = c("(M13)", "(M14)", "(M15)", "(M16)", "(M17)", "(M18)", "(M19)", "(M20)", "(M21)", "(M22)", "(M23)", "(M24)"),
          covariate.labels = c("Unemployed", "Lagged Unemployed", "UE:Lagged UE", "Age", "Education", "Member"),
          dep.var.labels = c("trust in government", "statisfaction with democracy", "life satisfaction", "trust in government", "satisfaction with democracy", "life satisfaction"),
          model.names = FALSE,
          model.numbers = FALSE,
          order = c(1,2,6,3,4,5)
          )
```

@@

shp.fit.wfe.tig.ext <- wfe(trust_in_government ~ unemployed * lagged_unemployed, 
                        data = shp,
                        treat = "unemployed",
                       unit.index = "unit", time.index = "time", method = "unit",
               qoi = "ate", estimator =NULL, hetero.se=TRUE, auto.se=TRUE,
               White = TRUE, White.alpha = 0.05, verbose = TRUE)

shp.fit.wfe.swd.ext <- wfe(satisfaction_with_democracy ~ unemployed * lagged_unemployed, 
                        data = shp,
                        treat = "unemployed",
                       unit.index = "unit", time.index = "time", method = "unit",
               qoi = "ate", estimator =NULL, hetero.se=TRUE, auto.se=TRUE,
               White = TRUE, White.alpha = 0.05, verbose = TRUE)

shp.fit.wfe.ls.ext <- wfe(life_satisfaction ~ unemployed * lagged_unemployed, 
                        data = shp,
                        treat = "unemployed",
                      unit.index = "unit", time.index = "time", method = "unit",
               qoi = "ate", estimator =NULL, hetero.se=TRUE, auto.se=TRUE,
               White = TRUE, White.alpha = 0.05, verbose = TRUE)

@@

liss.fit.wfe.tig.ext <- wfe(trust_in_government ~ unemployed * lagged_unemployed, 
                        data = liss,
                        treat = "unemployed",
                        unit.index = "unit", time.index = "time", method = "unit",
               qoi = "ate", estimator =NULL, hetero.se=TRUE, auto.se=TRUE,
               White = TRUE, White.alpha = 0.05, verbose = TRUE)

liss.fit.wfe.swd.ext <- wfe(satisfaction_with_democracy ~ unemployed * lagged_unemployed, 
                        data = liss,
                        treat = "unemployed",
                        unit.index = "unit", time.index = "time", method = "unit",
               qoi = "ate", estimator =NULL, hetero.se=TRUE, auto.se=TRUE,
               White = TRUE, White.alpha = 0.05, verbose = TRUE)

liss.fit.wfe.ls.ext <- wfe(life_satisfaction ~ unemployed * lagged_unemployed, 
                        data = liss,
                        treat = "unemployed",
                       unit.index = "unit", time.index = "time", method = "unit",
               qoi = "ate", estimator =NULL, hetero.se=TRUE, auto.se=TRUE,
               White = TRUE, White.alpha = 0.05, verbose = TRUE)

@@

```{r stargazer data}
wfe_regression_data <- data.frame(
  c1 = as.numeric(summary(shp.fit.wfe.tig.ext)[2]$coefficients[,1]),
  c2 = as.numeric(summary(shp.fit.wfe.swd.ext)[2]$coefficients[,1]),
  c3 = as.numeric(summary(shp.fit.wfe.ls.ext)[2]$coefficients[,1]),
  c4 = as.numeric(summary(liss.fit.wfe.tig.ext)[2]$coefficients[,1]),
  c5 = as.numeric(summary(liss.fit.wfe.swd.ext)[2]$coefficients[,1]),
  c6 = as.numeric(summary(liss.fit.wfe.ls.ext)[2]$coefficients[,1]),
  se1 = as.numeric(summary(shp.fit.wfe.tig.ext)[2]$coefficients[,2]),
  se2 = as.numeric(summary(shp.fit.wfe.swd.ext)[2]$coefficients[,2]),
  se3 = as.numeric(summary(shp.fit.wfe.ls.ext)[2]$coefficients[,2]),
  se4 = as.numeric(summary(liss.fit.wfe.tig.ext)[2]$coefficients[,2]),
  se5 = as.numeric(summary(liss.fit.wfe.swd.ext)[2]$coefficients[,2]),
  se6 = as.numeric(summary(liss.fit.wfe.ls.ext)[2]$coefficients[,2]),
  t1 = as.numeric(summary(shp.fit.wfe.tig.ext)[2]$coefficients[,3]),
  t2 = as.numeric(summary(shp.fit.wfe.swd.ext)[2]$coefficients[,3]),
  t3 = as.numeric(summary(shp.fit.wfe.ls.ext)[2]$coefficients[,3]),
  t4 = as.numeric(summary(liss.fit.wfe.tig.ext)[2]$coefficients[,3]),
  t5 = as.numeric(summary(liss.fit.wfe.swd.ext)[2]$coefficients[,3]),
  t6 = as.numeric(summary(liss.fit.wfe.ls.ext)[2]$coefficients[,3]),
  p1 = as.numeric(summary(shp.fit.wfe.tig.ext)[2]$coefficients[,4]),
  p2 = as.numeric(summary(shp.fit.wfe.swd.ext)[2]$coefficients[,4]),
  p3 = as.numeric(summary(shp.fit.wfe.ls.ext)[2]$coefficients[,4]),
  p4 = as.numeric(summary(liss.fit.wfe.tig.ext)[2]$coefficients[,4]),
  p5 = as.numeric(summary(liss.fit.wfe.swd.ext)[2]$coefficients[,4]),
  p6 = as.numeric(summary(liss.fit.wfe.ls.ext)[2]$coefficients[,4])
) %>%
  insertRows(3:5)
```

@@

  stargazer(p1, p1, p2, p2, p3, p3, p1, p1, p2, p2, p3, p3,
    order = c(1,2,6,3,4,5),
    coef = list(wfe_regression_data$c1,
                as.numeric(summary(shp.fit.wfe.control.tig.ext)[2]$coefficients[,1]),
                wfe_regression_data$c2,
                as.numeric(summary(shp.fit.wfe.control.swd.ext)[2]$coefficients[,1]),
                wfe_regression_data$c3,
                as.numeric(summary(shp.fit.wfe.control.ls.ext)[2]$coefficients[,1]),

                wfe_regression_data$c4,
                as.numeric(summary(liss.fit.wfe.control.tig.ext)[2]$coefficients[,1]),
                wfe_regression_data$c5,
                as.numeric(summary(liss.fit.wfe.control.swd.ext)[2]$coefficients[,1]),
                wfe_regression_data$c6,
                as.numeric(summary(liss.fit.wfe.control.ls.ext)[2]$coefficients[,1])

                ),
    se = list(wfe_regression_data$se1,
                as.numeric(summary(shp.fit.wfe.control.tig.ext)[2]$coefficients[,2]),
                wfe_regression_data$se2,
                as.numeric(summary(shp.fit.wfe.control.swd.ext)[2]$coefficients[,2]),
                wfe_regression_data$se3,
                as.numeric(summary(shp.fit.wfe.control.ls.ext)[2]$coefficients[,2]),

                wfe_regression_data$se4,
                as.numeric(summary(liss.fit.wfe.control.tig.ext)[2]$coefficients[,2]),
                wfe_regression_data$se5,
                as.numeric(summary(liss.fit.wfe.control.swd.ext)[2]$coefficients[,2]),
                wfe_regression_data$se6,
                as.numeric(summary(liss.fit.wfe.control.ls.ext)[2]$coefficients[,2])
              ),
    t = list(wfe_regression_data$t1,
                as.numeric(summary(shp.fit.wfe.control.tig.ext)[2]$coefficients[,3]),
                wfe_regression_data$t2,
                as.numeric(summary(shp.fit.wfe.control.swd.ext)[2]$coefficients[,3]),
                wfe_regression_data$t3,
                as.numeric(summary(shp.fit.wfe.control.ls.ext)[2]$coefficients[,3]),

                wfe_regression_data$t4,
                as.numeric(summary(liss.fit.wfe.control.tig.ext)[2]$coefficients[,3]),
                wfe_regression_data$t5,
                as.numeric(summary(liss.fit.wfe.control.swd.ext)[2]$coefficients[,3]),
                wfe_regression_data$t6,
                as.numeric(summary(liss.fit.wfe.control.ls.ext)[2]$coefficients[,3])

             ),  
    p = list(wfe_regression_data$p1,
                as.numeric(summary(shp.fit.wfe.control.tig.ext)[2]$coefficients[,4]),
                wfe_regression_data$p2,
                as.numeric(summary(shp.fit.wfe.control.swd.ext)[2]$coefficients[,4]),
                wfe_regression_data$p3,
                as.numeric(summary(shp.fit.wfe.control.ls.ext)[2]$coefficients[,4]),

                wfe_regression_data$p4,
                as.numeric(summary(liss.fit.wfe.control.tig.ext)[2]$coefficients[,4]),
                wfe_regression_data$p5,
                as.numeric(summary(liss.fit.wfe.control.swd.ext)[2]$coefficients[,4]),
                wfe_regression_data$p6,
                as.numeric(summary(liss.fit.wfe.control.ls.ext)[2]$coefficients[,4])
             ),  
    type = "latex",
    out="./extension-table-3.tex",
    omit.stat = "all",
    notes = "SEs in parentheses. Columns 25-30 are from the SHP survey and columns 31-36 are from the LISS survey.",
    notes.append = TRUE,
    font.size = "tiny",
    digits = 2,
    column.sep.width = "-10pt", 
    title = "SHP Switzerland and LISS Netherlands: weighted fixed effects models",
    digit.separator="",
    rownames = FALSE,
    column.labels = c("(M25)", "(M26)", "(M27)", "(M28)", "(M29)", "(M30)", "(M31)", "(M32)", "(M33)", "(M34)", "(M35)", "(M36)"), 
    model.names = FALSE,
    model.numbers = FALSE,
    star.cutoffs=c(0.05,0.01,0.001),
    covariate.labels = c("Unemployed", "Lagged Unemployed", "UE:Lagged UE", "Age", "Education", "Member"),
    dep.var.labels = c("trust in government", "statisfaction with democracy", "life satisfaction", "trust in government", "satisfaction with democracy", "life satisfaction"),
    header = FALSE
    )  
```

### 2020-05-05 paper.Rmd
making progress

---
title: "GOV 1006: Milestone 8"
subtitle: "Paper Replication Rough Draft"
author: "Pieter Quinton"
date: "4/17/2020"
abstract: "Bauer (2018) finds that there is no consistent relationship between unemployment and one's trust in government or their satisfaction with democracy. I was able to completely replicate the majority of his findings aside from a summary table of the data. My extension evaluates how consistent or long-term unemployment may impact one's views. Rather than examining the effects of just a single year of unemployment, as Bauer did, I track unemployement trends over longer periods of time to see if extended periods of unemployment have a stronger impact on one's feelings towards the government and its institutions than shorter periods of unemployment do."
output: 
  bookdown::pdf_document2:
    keep_tex: true
    toc: no
document_class: article
bibliography: milestone5_bib.bib
mainfont: Wingdings
sansfont: Wingdings
fontsize: 12pt
---

@@

Because were are unable to control for all observable and unobservable confounding variables arising from time and household variation, the second regression, displayed in Table 2, makes use of a fixed effects model. There are strong differences between the pooled model and the fixed effects model. The size of the coefficients has dropped across all of the covariates by a considerable amount. As such, fewer coefficients are statistically significant. Unemployed is no longer statistically significant, aside from the life satisfaction questions. Lagged unemployed remains statistically significant for satisfaction with democracy while the interaction term is only statistically significant for life satisfaction.

>>>>

---
title: "Unemployment Effects"
subtitle: "GOV 1006: Paper Replication"
author: "Pieter Quinton"
date: "4/17/2020"
abstract: "Bauer (2018) finds that there is no consistent relationship between unemployment and one's trust in government or their satisfaction with democracy. I was able to completely replicate the majority of his findings aside from a summary table of the data. My extension evaluates how consistent or long-term unemployment may impact one's views. Rather than examining the effects of just a single year of unemployment, as Bauer did, I track unemployement trends over longer periods of time to see if extended periods of unemployment have a stronger impact on one's feelings towards the government and its institutions than shorter periods of unemployment do."
output: 
  bookdown::pdf_document2:
    keep_tex: true
    toc: no
document_class: article
bibliography: milestone5_bib.bib
mainfont: Wingdings
sansfont: Wingdings
fontsize: 12pt
---

@@

Because the data provided does not provide the ability to control for all observable and unobservable confounding variables arising from time and household variation, the second regression, displayed in Table 2, makes use of a fixed effects model. There are strong differences between the pooled model and the fixed effects model. The size of the coefficients has dropped across all of the covariates by a considerable amount. As such, fewer coefficients are statistically significant. Unemployed is no longer statistically significant, aside from the life satisfaction questions. Lagged unemployed remains statistically significant for satisfaction with democracy while the interaction term is only statistically significant for life satisfaction.
